# NONMEM 설치하는 법


# Abstract

TBD

# Introduction

TBD

# Materials and Methods

TBD


# Results 

$\theta, \eta, \epsilon$ 개수를 먼저 지정해 주고 초기값을 설정합니다.

```{r}
DataAll = Theoph
colnames(DataAll) = c("ID", "BWT", "DOSE", "TIME", "DV")
DataAll[,"ID"] = as.numeric(as.character(DataAll[,"ID"]))

nTheta = 3
nEta = 3
nEps = 2

THETAinit = c(2, 50, 0.1)
OMinit = matrix(c(0.2, 0.1, 0.1, 0.1, 0.2, 0.1, 0.1, 0.1, 0.2), nrow=nEta, ncol=nEta)
SGinit = diag(c(0.1, 0.1))

LB = rep(0, nTheta) # Lower bound
UB = rep(1000000, nTheta) # Upper bound

FGD = deriv(~DOSE/(TH2*exp(ETA2))*TH1*exp(ETA1)/(TH1*exp(ETA1) - TH3*exp(ETA3))*
              (exp(-TH3*exp(ETA3)*TIME)-exp(-TH1*exp(ETA1)*TIME)),
            c("ETA1","ETA2","ETA3"),
            function.arg=c("TH1", "TH2", "TH3", "ETA1", "ETA2", "ETA3", "DOSE", "TIME"),
            func=TRUE,
            hessian=(e$METHOD == "LAPL"))
H = deriv(~F + F*EPS1 + EPS2, c("EPS1", "EPS2"), function.arg=c("F", "EPS1", "EPS2"), func=TRUE)

PRED = function(THETA, ETA, DATAi)
{
  FGDres = FGD(THETA[1], THETA[2], THETA[3], ETA[1], ETA[2], ETA[3], DOSE=320, DATAi[,"TIME"]) 
  Gres = attr(FGDres, "gradient")
  Hres = attr(H(FGDres, 0, 0), "gradient")
  
  if (e$METHOD == "LAPL") {
    Dres = attr(FGDres, "hessian")
    Res = cbind(FGDres, Gres, Hres, Dres[,1,1], Dres[,2,1], Dres[,2,2], Dres[,3,])
    colnames(Res) = c("F", "G1", "G2", "G3", "H1", "H2", "D11", "D21", "D22", "D31", "D32", "D33") 
  } else {
    Res = cbind(FGDres, Gres, Hres)
    colnames(Res) = c("F", "G1", "G2", "G3", "H1", "H2") 
  }
  return(Res)
}



```



####### First Order Approximation Method
InitStep(DataAll, THETAinit=THETAinit, OMinit=OMinit, SGinit=SGinit, LB=LB, UB=UB, 
         Pred=PRED, METHOD="ZERO")
(EstRes = EstStep())           # 4 sec
(CovRes = CovStep())           # 2 sec
PostHocEta() # Using e$FinalPara from EstStep()
TabStep()

## First Order Approximation Method

```{r}
InitStep(DataAll, THETAinit=THETAinit, OMinit=OMinit, SGinit=SGinit, LB=LB, UB=UB, 
         Pred=PRED, METHOD="ZERO")
```

먼저 `InitStep()`을 통해서 초기화를 합니다.

### EstRes

```{r}
(EstRes = EstStep())           # 4 sec
```

### CovRes

```{r}
(CovRes = CovStep())           # 2 sec
```

### PostHocEta

```{r}
PostHocEta() # FinalPara from EstStep()
```

### TabStep

```{r}
TabStep()
```


## First Order Conditional Estimation with Interaction Method

```{r eval = FALSE}
InitStep(DataAll, THETAinit=THETAinit, OMinit=OMinit, SGinit=SGinit, nTheta=nTheta, LB=LB, UB=UB, Pred=PRED, METHOD="COND")
(EstRes = EstStep())           # 1.7 min
(CovRes = CovStep())           # 44 sec
get("EBE", envir=e)
```

## Laplacian Approximation with Interacton Method

```{r eval = FALSE}
InitStep(DataAll, THETAinit=THETAinit, OMinit=OMinit, SGinit=SGinit, nTheta=nTheta, LB=LB, UB=UB, Pred=PRED, METHOD="LAPL")
(EstRes = EstStep())           # 3.4 min
(CovRes = CovStep())           # 52 sec
get("EBE", envir=e)
```


$$
G =
  \begin{bmatrix}
    \frac{\partial F}{\partial \eta_1} & \frac{\partial^2 F}{\partial \eta_1 \partial \eta_1}  & [blank] & [blank] \\
    \frac{F}{\eta_2} & \frac{\partial^2 F}{\partial \eta_2 \partial \eta_1} & \frac{\partial^2 F}{\partial \eta_2 \partial \eta_2} & [blank] \\
    \frac{F}{\eta_3} & \frac{\partial^2 F}{\partial \eta_3 \partial \eta_1} & \frac{\partial^2 F}{\partial \eta_3 \partial \eta_2} & \frac{\partial^2 F}{\partial \eta_3 \partial \eta_3}
  \end{bmatrix}
$$




```{r, echo = FALSE, eval = FALSE}
DiagrammeR::mermaid("
graph LR
A --> B
", height = 200)
```

# Discussion

# Acknowledgement

# References {-}

```{r, include = FALSE}
knitr::write_bib(file = 'bib/packages.bib')
```





